Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-03-27 paper/supplemental/cremi.tex
Update plots for the supplemental material.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiAtrails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on 5 sections of the CREMI A dataset. All measurements are reported as median VI, the lower the better. The threshold for automatic selection is $p_t=0.95$ (red line). The slope of the selection oracle shows that guided proofreading reduces VI faster.}
\label{fig:cremiAtrails}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiBtrails.pdf}
\caption{Split error correction by Plaza's focused proofreading and our guided proofreading compared on the CREMI B dataset. All measurements are reported as median VI, the lower the better. Automatic selection with threshold (red line) yields reasonable performance using guided proofreading.}
\label{fig:cremiBtrails}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiCtrails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the CREMI C dataset. Lower VI scores are better. Guided proofreading corrects the initial segmentation faster with less corrections than focused proofreading.}
\label{fig:cremiCtrails}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiA_trails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on 5 sections of the CREMI A dataset. All measurements are reported as median VI, the lower the better. The threshold for automatic selection is $p_t=0.95$ (green line). The slope of the selection oracle shows that guided proofreading reduces VI faster.}
\label{fig:cremiAtrails}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiB_trails.pdf}
\caption{Split error correction by Plaza's focused proofreading and our guided proofreading compared on the CREMI B dataset. All measurements are reported as median VI, the lower the better. Automatic selection with threshold (green line) yields reasonable performance using guided proofreading.}
\label{fig:cremiBtrails}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiC_trails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the CREMI C dataset. Lower VI scores are better. Guided proofreading corrects the initial segmentation faster with less corrections than focused proofreading. The green line shows the automatic threshold $p_t=0.95$.}
\label{fig:cremiCtrails}
\end{figure}

### 2017-03-27 paper/supplemental/leftcylinder.tex
Update plots for the supplemental material.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cyltrails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the L.~Cylinder dataset as reported in the paper. All measurements are shown as median VI, the lower the better. We compare automatic selection with threshold ($p_t=0.95$, red line) and the selection oracle for accepting or rejecting corrections using each method. Guided proofreading yields better results faster with fewer corrections.}
\label{fig:cyltrails}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cyl_trails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the L.~Cylinder dataset as reported in the paper. All measurements are shown as median VI, the lower the better. We compare automatic selection with threshold ($p_t=0.95$, green line) and the selection oracle for accepting or rejecting corrections using each method. Guided proofreading yields better results faster with fewer corrections.}
\label{fig:cyltrails}
\end{figure}
